Estimating the Effect of Eviction on Assessment Values

### 2023-03-15 writing/presentations/march_15.tex

\section{Introduction}
\begin{frame}{Introduction and Literature}
   \begin{enumerate}
       \item Eviction is a bigger problem in America than in other rich countries
       \begin{enumerate}
           \item Most poor renting families in America
spend over half of their incomes on rent (Desmond, 2017)
       \end{enumerate}
       \item Sociologists have found large effects of evictions using non-experimental methods
       \begin{enumerate}
           \item Increased probability of job loss (Desmond, Gershenson, 2016)
           \item Increased probability of depression (Desmond, Kimbro, 2015)
       \end{enumerate} 
       \item However, these estimates are likely confounded
       \begin{enumerate}
           \item ``Ashenfelter dip''
           \item Observable and unobservable confounders
       \end{enumerate}
       \item Only recently have economists began to apply quasi-experimental methods to study eviction
        \begin{enumerate}
            \item Van Dijk et al. find effects on durable consumption, access to credit, and more
        \end{enumerate}
   \end{enumerate}
\end{frame}

@@

\section{Data}
\begin{frame}{Data}
    \begin{enumerate}
        \item Eviction data from MassLandlords, a trade association
        \begin{enumerate}
            \item Scraped around 50,000 eviction case records
            \item Collects case outcome data, including method of resolution, judge name, and more
        \end{enumerate}
        \item Assessment values data from the Massachusetts Office of Geographic Information Services
        \begin{enumerate}
            \item Unbalanced panel data on assessor values for nearly every property in Massachussetts
        \end{enumerate}
        \item Link evictions to assessment records on fiscal year and location
    \end{enumerate}
\end{frame}

>>>>

\section{Introduction}
\begin{frame}{Introduction and Literature}
   \begin{enumerate}
       \item Eviction is a bigger problem in America than in other rich countries
       \begin{enumerate}
           \item Most poor renting families in America
spend over half of their incomes on rent (Desmond, 2017)
       \end{enumerate}
       \item Sociologists have found large effects of evictions using non-experimental methods, but economists 
       \begin{enumerate}
           \item Increased probability of job loss (Desmond, Gershenson, 2016)
           \item Increased probability of depression (Desmond, Kimbro, 2015)
       \end{enumerate} 
       \item However, these estimates are likely confounded
       \begin{enumerate}
           \item ``Ashenfelter dip''
           \item Observable and unobservable confounders
       \end{enumerate}
       \item Only recently have economists began to apply quasi-experimental methods to study eviction
        \begin{enumerate}
            \item Van Dijk et al. find effects on durable consumption, access to credit, and more
        \end{enumerate}
   \end{enumerate}
\end{frame}

@@

\section{Data}
\begin{frame}{Data}
    \begin{enumerate}
        \item Eviction data from MassLandlords, a trade association
        \begin{enumerate}
            \item Scraped around 50,000 eviction case records
            \item Collects case outcome data, including method of resolution, judge name, and more
        \end{enumerate}
        \item Crime data from the Boston Police Department (BPD)
        \begin{enumerate}
            \item Incident-level data for every incident that BPD has responded to since 2015
            \item Coordinates of each incident
        \end{enumerate}
        \item Create 100m radius around every eviction and match to crimes which fall into that radius
    \end{enumerate}
\end{frame}
